Exploratory data analysis

### 2022-07-06 slides/data_checking.Rmd
add j recall acc by metamemory state per pereverseff

### Metamemory state counts

```{r}
j_meta %>%
  filter(!is.na(resp)) %>% 
  left_join(j_recall %>% select(subj_num, answer, acc_recall)) %>% 
  filter(acc_recall) %>% 
  ggplot(aes(x = subj_num, fill = resp)) +
  geom_bar() +
  labs(x = "Participant", y = "# facts labeled with that memory state", fill = "Memory state") +
  theme_bw() +
  theme(axis.text.x = element_blank(),
        legend.position = 0:1,
        legend.justification = 0:1,
        legend.background = element_blank())
```

>>>>

### Metamemory state counts (correct trials only!)

```{r}
j_meta %>%
  filter(!is.na(resp)) %>% 
  left_join(j_recall %>% select(subj_num, answer, acc_recall)) %>% 
  filter(acc_recall) %>% 
  ggplot(aes(x = subj_num, fill = resp)) +
  geom_bar() +
  labs(x = "Participant", y = "# correctly recalled facts labeled with that memory state", fill = "Memory state") +
  theme_bw() +
  theme(axis.text.x = element_blank(),
        legend.position = 0:1,
        legend.justification = 0:1,
        legend.background = element_blank())
```

### Recall accuracy by metamemory state

```{r}
j_recall %>%
  select(subj_num, j_score, question, answer, acc_recall) %>%
  left_join(j_meta %>% select(subj_num, question, answer, metamemory = resp),
            by = c("subj_num", "question", "answer")) %>%
  mutate(metamemory = coalesce(metamemory, "Don't Know")) %>%
  group_by(subj_num, metamemory) %>%
  summarize(acc = mean(acc_recall),
            n_trials = n()) %>%
  ggplot(aes(x = metamemory, y = acc)) +
  geom_boxplot()
```
